---
title: "Data Analysis and Visualization"
output: github_document
date: "Last updated: July 9, 2024"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Package Loading

Here, we list the packages that will be required to support our analytical and visualization procedures.

```{r}
library(tidyverse)
library(viridis)
library(RColorBrewer)
library(colorspace)
library(ggpubr)
library(ggridges)
library(forcats)
library(lazyeval)
```

# Data Loading

The below code chunk loads in the data in the two formats we specified at the end of our cleaning script: one suited for spatial visualization and analysis and one not. 

```{r}
impact_data <- read.csv("/Users/kenjinchang/github/university-impact-model/data/model-output/university-impact-model.csv")
spatial_impact_data <- read.csv("/Users/kenjinchang/github/university-impact-model/data/model-output/university-impact-model-shapefile.csv")
```

# Methods-Section Figures

## Nation-State Inclusion 

As specified in the manuscript, we will need to generate a figure separating the nation-states included within our analysis from those that were omitted for the various reasons cited in our cleaning script. 

We will eventually also have to create a complementary flow diagram documenting this exclusion process, whereby nation-states were excluded either (1) because they did not have complete dietary-footprint data for the nine dietary scenarios across the two identified sources (i.e., publication data for Kim et al. (2020) and publication data for Semba et al. (2020)), (2) because they did not have the ___

For now, we focus on creating a choropleth map using `spatial_impact_data` indicating which and how many nation-states are being factored into our country-level and global results.

```{r}
spatial_impact_data <- spatial_impact_data %>%
  mutate(inclusion=case_when(university_enrollment>0~"Included")) 
impact_data<- impact_data %>%
  mutate(inclusion=case_when(university_enrollment>0~"Included")) 
```


```{r}
ggplot(spatial_impact_data,aes(x=long,y=lat,fill=inclusion,group=group)) + 
  geom_polygon(color="black",linewidth=0.125) +
  scale_fill_brewer(palette="Pastel2",na.value="white",name="Inclusion Outcomes",labels=c("Included (n=120)","NA")) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

# Descriptive Results

## Enrollment Indicators

To provide readers with a sense of  scale and context, we perform a series of calculations to derive a few relevant statistics. These include:

* The mean proportion of the national population that is between the ages of 18 and 23 across the 120 included nation-states (i.e., 7.30%)

```{r}
impact_data %>%
  select(country,proportion_school_aged) %>%
  summarise(mean(proportion_school_aged))
```
* The mean proportion of the school-aged population that is thought to be enrolled in college or university programs across the 120 included nation-states (i.e., 41.50%)

```{r}
impact_data %>%
  select(country,proportion_school_aged_enrolled) %>%
  summarise(mean(proportion_school_aged_enrolled))
```

* The global sum of people enrolled in college and university programs across the 120 included nation-states (i.e., 168,167,205)

```{r}
impact_data %>%
  summarize(sum(university_enrollment))
```

* The global sum of people of all ages residing in the 120 included nation-states (i.e., 6,592,823,027)

```{r}
impact_data %>%
  summarise(sum(national_population))
```

* The proportion of that sum enrollees account for (i.e., 2.55%)

```{r}
168167205 / 6592823027
```

This final statistic, in particular, will provide us with a more complete understanding of the size and proportion of the population that the expected reductions in carbon emissions are being modeled from. 

```{r}
impact_data %>% 
  ggplot(aes(university_enrollment,proportion_school_aged_enrolled,label=country_alpha_three,color=per_capita_gni)) + 
  geom_point() + 
  scale_color_gradient(low="mistyrose1",high="salmon4",na.value="white",name="Per Capita \nGross National Income",guide=guide_colourbar(reverse=FALSE,title.position="top",title.hjust=0)) +
  geom_text(color="black",hjust=-0.15,nudge_x=0.05,alpha=0.6) +
  xlab("College and University Enrollment") + 
  ylab("Proportion School-Aged Enrolled") +
  theme(legend.key.width=unit(1,"lines"),legend.position="right",legend.justification="left",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
university_enrollment_absolute <- spatial_impact_data %>%
  ggplot(aes(x=long,y=lat,fill=university_enrollment,group=group)) + 
  geom_polygon(color="black",linewidth=0.125,alpha=0.8) +
  scale_fill_gradient(low="lavender",high="darkslateblue",na.value="white",name="Enrollment in College and University Programs",guide=guide_colourbar(reverse=FALSE,title.position="top",title.hjust=0.5)) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  theme(legend.key.width=unit(3,"lines"),legend.position="bottom",legend.justification="center",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
university_enrollment_relative <- spatial_impact_data %>%
  ggplot(aes(x=long,y=lat,fill=proportion_school_aged_enrolled,group=group)) + 
  geom_polygon(color="black",linewidth=0.125,alpha=0.8) +
  scale_fill_gradient(low="lavender",high="darkslateblue",na.value="white",name="Proportion of School-Aged Population Enrolled",guide=guide_colourbar(reverse=FALSE,title.position="top",title.hjust=0.5)) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  theme(legend.key.width=unit(3,"lines"),legend.position="bottom",legend.justification="center",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(university_enrollment_absolute,university_enrollment_relative,
          nrow=2,
          labels=c("A","B"))
```

## Lending- and Development-Group Membership

```{r}
impact_data %>%
  count(lending_group)
```

```{r}
impact_data %>%
  count(development_group)
```

```{r}
lending_group_membership <- spatial_impact_data %>%
  ggplot(aes(x=long,y=lat,group=group,fill=factor(lending_group,levels=c("Low","Lower-Middle","Upper-Middle","High","NA")))) + 
  geom_polygon(color="black",linewidth=0.125) +
  scale_fill_brewer(palette="Set2",na.value="white",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_membership <- spatial_impact_data %>%
  ggplot(aes(x=long,y=lat,group=group,fill=factor(development_group,levels=c("Low","Medium","High","Very High","NA")))) + 
  geom_polygon(color="black",linewidth=0.125) +
  scale_fill_brewer(palette="Set3",na.value="white",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_membership,development_group_membership,
          nrow=2,
          labels=c("A","B"))
```

## Technical Potential

Because the mean reduction across the nine dietary change scenarios may not be particularly meaningful, we may want to, instead, look at the returns associated with the scenario yielding the greatest reductions, instead.

For now, though, let us look at each scenario, individually.

### Meatless Day

```{r}
lending_group_meatless_day_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,meatless_day_population_reduction_kg_co2e),y=meatless_day_population_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
lending_group_meatless_day_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,meatless_day_population_percent_reduction_kg_co2e),y=meatless_day_population_percent_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_meatless_day_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,meatless_day_population_reduction_kg_co2e),y=meatless_day_population_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_meatless_day_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,meatless_day_population_percent_reduction_kg_co2e),y=meatless_day_population_percent_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_meatless_day_absolute_reduction,development_group_meatless_day_absolute_reduction,lending_group_meatless_day_relative_reduction,development_group_meatless_day_relative_reduction,
          nrow=2,
          ncol=2,
          labels=c("A","B","C","D"))
```

```{r}
impact_data %>%
  summarise(mean(meatless_day_population_reduction_kg_co2e))
```

```{r}
impact_data %>%
  summarise(mean(meatless_day_population_percent_reduction_kg_co2e))
```

### Low Red Meat

```{r}
lending_group_low_red_meat_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,low_red_meat_population_reduction_kg_co2e),y=low_red_meat_population_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
lending_group_low_red_meat_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,low_red_meat_population_percent_reduction_kg_co2e),y=low_red_meat_population_percent_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_low_red_meat_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,low_red_meat_population_reduction_kg_co2e),y=low_red_meat_population_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_low_red_meat_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,low_red_meat_population_percent_reduction_kg_co2e),y=low_red_meat_population_percent_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_low_red_meat_absolute_reduction,development_group_low_red_meat_absolute_reduction,lending_group_low_red_meat_relative_reduction,development_group_low_red_meat_relative_reduction,
          nrow=2,
          ncol=2,
          labels=c("A","B","C","D"))
```
```{r}
impact_data %>%
  summarise(mean(low_red_meat_population_reduction_kg_co2e))
```

```{r}
impact_data %>%
  summarise(mean(low_red_meat_population_percent_reduction_kg_co2e))
```

### No Red Meat

```{r}
lending_group_no_red_meat_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,no_red_meat_population_reduction_kg_co2e),y=no_red_meat_population_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
lending_group_no_red_meat_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,no_red_meat_population_percent_reduction_kg_co2e),y=no_red_meat_population_percent_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) +  
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_no_red_meat_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,no_red_meat_population_reduction_kg_co2e),y=no_red_meat_population_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_no_red_meat_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,no_red_meat_population_percent_reduction_kg_co2e),y=no_red_meat_population_percent_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_no_red_meat_absolute_reduction,development_group_no_red_meat_absolute_reduction,lending_group_no_red_meat_relative_reduction,development_group_no_red_meat_relative_reduction,
          nrow=2,
          ncol=2,
          labels=c("A","B","C","D"))
```

```{r}
impact_data %>%
  summarise(mean(no_red_meat_population_reduction_kg_co2e))
```

```{r}
impact_data %>%
  summarise(mean(no_red_meat_population_percent_reduction_kg_co2e))
```

### No Dairy

```{r}
lending_group_no_dairy_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,no_dairy_population_reduction_kg_co2e),y=no_dairy_population_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
lending_group_no_dairy_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,no_dairy_population_percent_reduction_kg_co2e),y=no_dairy_population_percent_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_no_dairy_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,no_dairy_population_reduction_kg_co2e),y=no_dairy_population_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_no_dairy_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,no_dairy_population_percent_reduction_kg_co2e),y=no_dairy_population_percent_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_no_dairy_absolute_reduction,development_group_no_dairy_absolute_reduction,lending_group_no_dairy_relative_reduction,development_group_no_dairy_relative_reduction,
          nrow=2,
          ncol=2,
          labels=c("A","B","C","D"))
```

```{r}
impact_data %>%
  summarise(mean(no_dairy_population_reduction_kg_co2e))
```

```{r}
impact_data %>%
  summarise(mean(no_dairy_population_percent_reduction_kg_co2e))
```

### Pescetarian

```{r}
lending_group_pescetarian_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,pescetarian_population_reduction_kg_co2e),y=pescetarian_population_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
lending_group_pescetarian_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,pescetarian_population_percent_reduction_kg_co2e),y=pescetarian_population_percent_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_pescetarian_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,pescetarian_population_reduction_kg_co2e),y=pescetarian_population_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_pescetarian_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,pescetarian_population_percent_reduction_kg_co2e),y=pescetarian_population_percent_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_pescetarian_absolute_reduction,development_group_pescetarian_absolute_reduction,lending_group_pescetarian_relative_reduction,development_group_pescetarian_relative_reduction,
          nrow=2,
          ncol=2,
          labels=c("A","B","C","D"))
```
```{r}
impact_data %>%
  summarise(mean(pescetarian_population_reduction_kg_co2e))
```

```{r}
impact_data %>%
  summarise(mean(pescetarian_population_percent_reduction_kg_co2e))
```

### Lacto-Ovo Vegetarian

```{r}
lending_group_lacto_ovo_vegetarian_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,lacto_ovo_vegetarian_population_reduction_kg_co2e),y=lacto_ovo_vegetarian_population_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
lending_group_lacto_ovo_vegetarian_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,lacto_ovo_vegetarian_population_percent_reduction_kg_co2e),y=lacto_ovo_vegetarian_population_percent_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_lacto_ovo_vegetarian_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,lacto_ovo_vegetarian_population_reduction_kg_co2e),y=lacto_ovo_vegetarian_population_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_lacto_ovo_vegetarian_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,lacto_ovo_vegetarian_population_percent_reduction_kg_co2e),y=lacto_ovo_vegetarian_population_percent_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_lacto_ovo_vegetarian_absolute_reduction,development_group_lacto_ovo_vegetarian_absolute_reduction,lending_group_lacto_ovo_vegetarian_relative_reduction,development_group_lacto_ovo_vegetarian_relative_reduction,
          nrow=2,
          ncol=2,
          labels=c("A","B","C","D"))
```

```{r}
impact_data %>%
  summarise(mean(lacto_ovo_vegetarian_population_reduction_kg_co2e))
```

```{r}
impact_data %>%
  summarise(mean(lacto_ovo_vegetarian_population_percent_reduction_kg_co2e))
```

### EAT-Lancet

```{r}
lending_group_eat_lancet_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,eat_lancet_population_reduction_kg_co2e),y=eat_lancet_population_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
lending_group_eat_lancet_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,eat_lancet_population_percent_reduction_kg_co2e),y=eat_lancet_population_percent_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_eat_lancet_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,eat_lancet_population_reduction_kg_co2e),y=eat_lancet_population_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_eat_lancet_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,eat_lancet_population_percent_reduction_kg_co2e),y=eat_lancet_population_percent_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_eat_lancet_absolute_reduction,development_group_eat_lancet_absolute_reduction,lending_group_eat_lancet_relative_reduction,development_group_eat_lancet_relative_reduction,
          nrow=2,
          ncol=2,
          labels=c("A","B","C","D"))
```

```{r}
impact_data %>%
  summarise(mean(eat_lancet_population_reduction_kg_co2e))
```

```{r}
impact_data %>%
  summarise(mean(eat_lancet_population_percent_reduction_kg_co2e))
```

### Two-Thirds Vegan

```{r}
lending_group_two_thirds_vegan_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,two_thirds_vegan_population_reduction_kg_co2e),y=two_thirds_vegan_population_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
lending_group_two_thirds_vegan_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,two_thirds_vegan_population_percent_reduction_kg_co2e),y=two_thirds_vegan_population_percent_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_two_thirds_vegan_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,two_thirds_vegan_population_reduction_kg_co2e),y=two_thirds_vegan_population_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_two_thirds_vegan_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,two_thirds_vegan_population_percent_reduction_kg_co2e),y=two_thirds_vegan_population_percent_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_two_thirds_vegan_absolute_reduction,development_group_two_thirds_vegan_absolute_reduction,lending_group_two_thirds_vegan_relative_reduction,development_group_two_thirds_vegan_relative_reduction,
          nrow=2,
          ncol=2,
          labels=c("A","B","C","D"))
```

```{r}
impact_data %>%
  summarise(mean(two_thirds_vegan_population_reduction_kg_co2e))
```

```{r}
impact_data %>%
  summarise(mean(two_thirds_vegan_population_percent_reduction_kg_co2e))
```

### Vegan 

```{r}
lending_group_vegan_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,vegan_population_reduction_kg_co2e),y=vegan_population_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
lending_group_vegan_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,vegan_population_percent_reduction_kg_co2e),y=vegan_population_percent_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_vegan_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,vegan_population_reduction_kg_co2e),y=vegan_population_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_vegan_relative_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,vegan_population_percent_reduction_kg_co2e),y=vegan_population_percent_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_vegan_absolute_reduction,development_group_vegan_absolute_reduction,lending_group_vegan_relative_reduction,development_group_vegan_relative_reduction,
          nrow=2,
          ncol=2,
          labels=c("A","B","C","D"))
```

```{r}
impact_data %>%
  summarise(mean(vegan_population_reduction_kg_co2e))
```

```{r}
impact_data %>%
  summarise(mean(vegan_population_percent_reduction_kg_co2e))
```

### Distributions of countries across diets, not split by income group (but can use color points to represent)

```{r}
impact_data %>%
  select(country,lending_group,development_group,meatless_day_population_reduction_kg_co2e,low_red_meat_population_reduction_kg_co2e,no_red_meat_population_reduction_kg_co2e,no_dairy_population_reduction_kg_co2e,pescetarian_population_reduction_kg_co2e,lacto_ovo_vegetarian_population_reduction_kg_co2e,eat_lancet_population_reduction_kg_co2e,two_thirds_vegan_population_reduction_kg_co2e,vegan_population_reduction_kg_co2e) %>%
  pivot_longer(cols=ends_with("kg_co2e"),names_to="diet",values_to="value") %>%
  ggplot(aes(x=value,y=diet,fill=diet,color=diet)) + 
  geom_violin(draw_quantiles=0.5,adjust=150,alpha=0.5) + 
  scale_fill_brewer(palette="Set3") + 
  scale_color_brewer(palette="Set3") +
  stat_summary(fun.y=mean,geom="point",shape=20,size=3,color="black",fill="white") +
  theme(legend.position="bottom")
```

```{r}
impact_data %>%
  select(country,lending_group,development_group,meatless_day_population_reduction_kg_co2e,low_red_meat_population_reduction_kg_co2e,no_red_meat_population_reduction_kg_co2e,no_dairy_population_reduction_kg_co2e,pescetarian_population_reduction_kg_co2e,lacto_ovo_vegetarian_population_reduction_kg_co2e,eat_lancet_population_reduction_kg_co2e,two_thirds_vegan_population_reduction_kg_co2e,vegan_population_reduction_kg_co2e) %>%
  pivot_longer(cols=ends_with("kg_co2e"),names_to="diet",values_to="value") %>%
  ggplot(aes(x=value,y=diet,fill=diet)) + 
  geom_boxplot(outlier.shape=NA) + 
  stat_summary(fun.y=mean,geom="point",shape=20,size=3,color="black",fill="white") +
  coord_cartesian(xlim=c(-500000000,3000000000)) +
  theme(legend.position="bottom")
```


```{r}
impact_data %>%
  select(country,lending_group,development_group,meatless_day_population_percent_reduction_kg_co2e,low_red_meat_population_percent_reduction_kg_co2e,no_red_meat_population_percent_reduction_kg_co2e,no_dairy_population_percent_reduction_kg_co2e,pescetarian_population_percent_reduction_kg_co2e,lacto_ovo_vegetarian_population_percent_reduction_kg_co2e,eat_lancet_population_percent_reduction_kg_co2e,two_thirds_vegan_population_percent_reduction_kg_co2e,vegan_population_percent_reduction_kg_co2e) %>%
  pivot_longer(cols=ends_with("kg_co2e"),names_to="diet",values_to="value" )%>%
  ggplot(aes(x=value,y=diet,fill=diet)) + 
  geom_boxplot(outlier.shape=NA) + 
  stat_summary(fun.y=mean,geom="point",shape=20,size=3,color="black",fill="white") +
  coord_cartesian(xlim=c(-1,1)) +
  theme(legend.position="bottom")
```



```{r}
impact_data %>%
  select(country,lending_group,development_group,meatless_day_population_percent_reduction_kg_co2e,low_red_meat_population_percent_reduction_kg_co2e,no_red_meat_population_percent_reduction_kg_co2e,no_dairy_population_percent_reduction_kg_co2e,pescetarian_population_percent_reduction_kg_co2e,lacto_ovo_vegetarian_population_percent_reduction_kg_co2e,eat_lancet_population_percent_reduction_kg_co2e,two_thirds_vegan_population_percent_reduction_kg_co2e,vegan_population_percent_reduction_kg_co2e) %>%
  pivot_longer(cols=ends_with("kg_co2e"),names_to="diet",values_to="value" )%>%
  ggplot(aes(x=value,y=diet,fill=diet)) + 
  geom_violin() + 
  stat_summary(fun.y=mean,geom="point",shape=20,size=3,color="black",fill="white") +
  theme(legend.position="bottom")
```

```{r}
impact_data %>%
  select(country,lending_group,development_group,meatless_day_population_percent_reduction_kg_co2e,low_red_meat_population_percent_reduction_kg_co2e,no_red_meat_population_percent_reduction_kg_co2e,no_dairy_population_percent_reduction_kg_co2e,pescetarian_population_percent_reduction_kg_co2e,lacto_ovo_vegetarian_population_percent_reduction_kg_co2e,eat_lancet_population_percent_reduction_kg_co2e,two_thirds_vegan_population_percent_reduction_kg_co2e,vegan_population_percent_reduction_kg_co2e) %>%
  pivot_longer(cols=ends_with("kg_co2e"),names_to="diet",values_to="value" )%>%
  ggplot(aes(value,fill=factor(diet,levels=c("meatless_day_population_percent_reduction_kg_co2e","low_red_meat_population_percent_reduction_kg_co2e","no_red_meat_population_percent_reduction_kg_co2e","no_dairy_population_percent_reduction_kg_co2e","pescetarian_population_percent_reduction_kg_co2e","lacto_ovo_vegetarian_population_percent_reduction_kg_co2e","eat_lancet_population_percent_reduction_kg_co2e","two_thirds_vegan_population_percent_reduction_kg_co2e","vegan_population_percent_reduction_kg_co2e")),color=factor(diet,levels=c("meatless_day_population_percent_reduction_kg_co2e","low_red_meat_population_percent_reduction_kg_co2e","no_red_meat_population_percent_reduction_kg_co2e","no_dairy_population_percent_reduction_kg_co2e","pescetarian_population_percent_reduction_kg_co2e","lacto_ovo_vegetarian_population_percent_reduction_kg_co2e","eat_lancet_population_percent_reduction_kg_co2e","two_thirds_vegan_population_percent_reduction_kg_co2e","vegan_population_percent_reduction_kg_co2e")))) + 
  geom_density(alpha=0.4) + 
  theme(legend.position="bottom")
```


### Optimized

As described previously, we will now run a similar set of analyses for the 120 included nation-states - this time, for each of their optimal change scenarios. - should spot check this

```{r}
impact_data <- impact_data %>%
  mutate(greatest_population_reduction_kg_co2e=pmax(baseline_population_reduction_kg_co2e,baseline_adjusted_population_reduction_kg_co2e,baseline_oecd_population_reduction_kg_co2e,meatless_day_population_reduction_kg_co2e,low_red_meat_population_reduction_kg_co2e,no_red_meat_population_reduction_kg_co2e,no_dairy_population_reduction_kg_co2e,pescetarian_population_reduction_kg_co2e,lacto_ovo_vegetarian_population_reduction_kg_co2e,eat_lancet_population_reduction_kg_co2e,two_thirds_vegan_population_reduction_kg_co2e,vegan_population_reduction_kg_co2e))
```

```{r}
impact_data <- impact_data %>%
  mutate(greatest_reduction_diet=case_when(greatest_population_reduction_kg_co2e==baseline_population_reduction_kg_co2e~"Baseline",
  greatest_population_reduction_kg_co2e==baseline_adjusted_population_reduction_kg_co2e~"Baseline Adjusted",
  greatest_population_reduction_kg_co2e==baseline_oecd_population_reduction_kg_co2e~"Baseline OECD",
  greatest_population_reduction_kg_co2e==meatless_day_population_reduction_kg_co2e~"Meatless Day",
  greatest_population_reduction_kg_co2e==low_red_meat_population_reduction_kg_co2e~"Low Red Meat",
  greatest_population_reduction_kg_co2e==no_red_meat_population_reduction_kg_co2e~"No Red Meat",
  greatest_population_reduction_kg_co2e==no_dairy_population_reduction_kg_co2e~"No Dairy",
  greatest_population_reduction_kg_co2e==pescetarian_population_reduction_kg_co2e~"Pescetarian",
  greatest_population_reduction_kg_co2e==lacto_ovo_vegetarian_population_reduction_kg_co2e~"Lacto-Ovo Vegetarian",
  greatest_population_reduction_kg_co2e==eat_lancet_population_reduction_kg_co2e~"EAT Lancet",
  greatest_population_reduction_kg_co2e==two_thirds_vegan_population_reduction_kg_co2e~"Two-Thirds Vegan",
  greatest_population_reduction_kg_co2e==vegan_population_reduction_kg_co2e~"Vegan"))
```


```{r}
impact_data %>%
  select(country,greatest_population_reduction_kg_co2e) %>%
  arrange(desc(greatest_population_reduction_kg_co2e)) %>%
  head(10)
```


With this complete, we can now calculate the "technical potential" of university-based dietary interventions, which is to say, the total reductions in diet-attributable greenhouse gas emission (represented in kg CO2e) if the target populations were to change their behaviors as intended, per Nielsen and colleagues (2024).

```{r}
impact_data %>%
  summarize(sum(greatest_population_reduction_kg_co2e))
```
We can also identify the top 10 performing nation-states, as we did before - this time, for the optimized scenarios.

```{r}
impact_data %>%
  select(country,greatest_population_reduction_kg_co2e) %>%
  arrange(desc(greatest_population_reduction_kg_co2e)) %>%
  head(10)
```

Will have to move this to the most appropriate section later, BUT, we'll want to use similar code to look at how this varies across groupings 

```{r}
impact_data %>%
  select(country,lending_group,greatest_population_reduction_kg_co2e) %>%
  group_by(lending_group) %>%
  arrange(desc(greatest_population_reduction_kg_co2e)) 
```


estimates the total global impact if the most ideal dietary change occurred - should do same for relative change (percent reduction)

```{r}
lending_group_optimized_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,greatest_population_reduction_kg_co2e),y=greatest_population_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```
  
```{r}
development_group_optimized_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,greatest_population_reduction_kg_co2e),y=greatest_population_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```
  
```{r}
ggarrange(lending_group_optimized_absolute_reduction,development_group_optimized_absolute_reduction,
          nrow=2,
          labels=c("A","B"))
```

```{r}
lending_group_optimized_percent_reduction <- impact_data %>% 
  mutate(optimal_diet_population_percent_reduction_kg_co2e=(baseline_population_kg_co2e-greatest_population_reduction_kg_co2e)/baseline_population_kg_co2e) %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,optimal_diet_population_percent_reduction_kg_co2e),y=optimal_diet_population_percent_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Average Percent-Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_optimized_percent_reduction <- impact_data %>% 
  mutate(optimal_diet_population_percent_reduction_kg_co2e=(baseline_population_kg_co2e-greatest_population_reduction_kg_co2e)/baseline_population_kg_co2e) %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,optimal_diet_population_percent_reduction_kg_co2e),y=optimal_diet_population_percent_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Average Percent-Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_optimized_percent_reduction,development_group_optimized_percent_reduction,
          nrow=2,
          labels=c("A","B"))
```
 
Might be good to spot check after changing percent-decrease calculation in cleaning script, now that vegan is not mirrored with optimal

```{r}
impact_data %>%
  mutate(optimal_diet_population_percent_reduction_kg_co2e=(baseline_population_kg_co2e-greatest_population_reduction_kg_co2e)/baseline_population_kg_co2e) %>%
  select(country,vegan_population_percent_reduction_kg_co2e,optimal_diet_population_percent_reduction_kg_co2e,vegan_population_reduction_kg_co2e,greatest_population_reduction_kg_co2e) %>%
  head(10)
```


NEXT STEP WILL BE TO LOOK AT RELATIVE CHANGE FROM OPTIMIZED SCENARIO AND ALSO PROBABLY MOVE DICHOTOMIZED TO LOWER SECTIONS - 
  
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  
  
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 

xlab("Nation-State") + 
  ylab("Average Reduction in Diet-Attributable Emissions") + 
  
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))



## Lending- and Development-Group Distributions

First, change population figures to millions kg Co2e

```{r}
impact_data <- impact_data %>%
  mutate(baseline_population_kg_co2e=baseline_population_kg_co2e/1000000) %>%
  mutate(baseline_adjusted_population_kg_co2e=baseline_adjusted_population_kg_co2e/1000000) %>%
  mutate(baseline_oecd_population_kg_co2e=baseline_oecd_population_kg_co2e/1000000) %>%
  mutate(meatless_day_population_kg_co2e=meatless_day_population_kg_co2e/1000000) %>%
  mutate(low_red_meat_population_kg_co2e=low_red_meat_population_kg_co2e/1000000) %>%
  mutate(no_red_meat_population_kg_co2e=no_red_meat_population_kg_co2e/1000000) %>%
  mutate(no_dairy_population_kg_co2e=no_dairy_population_kg_co2e/1000000) %>%
  mutate(pescetarian_population_kg_co2e=pescetarian_population_kg_co2e/1000000) %>%
  mutate(lacto_ovo_vegetarian_population_kg_co2e=lacto_ovo_vegetarian_population_kg_co2e/1000000) %>%
  mutate(eat_lancet_population_kg_co2e=eat_lancet_population_kg_co2e/1000000) %>%
  mutate(two_thirds_vegan_population_kg_co2e=two_thirds_vegan_population_kg_co2e/1000000) %>%
  mutate(vegan_population_kg_co2e=vegan_population_kg_co2e/1000000) %>%
  mutate(baseline_adjusted_population_reduction_kg_co2e=baseline_adjusted_population_reduction_kg_co2e/1000000) %>%
  mutate(baseline_oecd_population_reduction_kg_co2e=baseline_oecd_population_reduction_kg_co2e/1000000) %>%
  mutate(meatless_day_population_reduction_kg_co2e=meatless_day_population_reduction_kg_co2e/1000000) %>%
  mutate(low_red_meat_population_reduction_kg_co2e=low_red_meat_population_reduction_kg_co2e/1000000) %>%
  mutate(no_red_meat_population_reduction_kg_co2e=no_red_meat_population_reduction_kg_co2e/1000000) %>%
  mutate(no_dairy_population_reduction_kg_co2e=no_dairy_population_reduction_kg_co2e/1000000) %>%
  mutate(pescetarian_population_reduction_kg_co2e=pescetarian_population_reduction_kg_co2e/1000000) %>%
  mutate(lacto_ovo_vegetarian_population_reduction_kg_co2e=lacto_ovo_vegetarian_population_reduction_kg_co2e/1000000) %>%
  mutate(eat_lancet_population_reduction_kg_co2e=eat_lancet_population_reduction_kg_co2e/1000000) %>%
  mutate(two_thirds_vegan_population_reduction_kg_co2e=two_thirds_vegan_population_reduction_kg_co2e/1000000) %>%
  mutate(vegan_population_reduction_kg_co2e=vegan_population_reduction_kg_co2e/1000000)
```


```{r}
lending_group_baseline_distribution <- impact_data %>%
  ggplot(aes(baseline_population_kg_co2e,fill=factor(lending_group,levels=c("Low","Lower-Middle","Upper-Middle","High","NA")),color=factor(lending_group,levels=c("Low","Lower-Middle","Upper-Middle","High","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) +
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  xlim(-800,2500) + 
  xlab(bquote('Annual Population-Level, Diet-Attributable Emissions at Baseline (Million kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_baseline_distribution <- impact_data %>%
  ggplot(aes(baseline_population_kg_co2e,fill=factor(development_group,levels=c("Low","Medium","High","Very High","NA")),color=factor(development_group,levels=c("Low","Medium","High","Very High","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) +
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  xlim(-400,1500) +
  xlab(bquote('Annual Population-Level, Diet-Attributable Emissions at Baseline (Million kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_baseline_distribution,development_group_baseline_distribution,
          nrow=2,
          labels=c("A","B"))
```


```{r}
impact_data %>%
  group_by(lending_group) %>%
  summarize(mean=mean(baseline_population_kg_co2e),sd=sd(baseline_population_kg_co2e)) 
```


```{r}
impact_data %>%
  group_by(development_group) %>%
  summarize(mean=mean(baseline_population_kg_co2e),sd=sd(baseline_population_kg_co2e)) 
```


## Groupwise Comparisons

```{r}
impact_data %>%
  group_by(lending_group) %>%
  summarize(mean=mean(greatest_population_reduction_kg_co2e),sd=sd(greatest_population_reduction_kg_co2e))
```

```{r}
impact_data %>%
  group_by(development_group) %>%
  summarize(mean=mean(greatest_population_reduction_kg_co2e),sd=sd(greatest_population_reduction_kg_co2e))
```

```{r}
lending_group_reductions_optimized <- impact_data %>%
  ggplot(aes(greatest_population_reduction_kg_co2e,fill=factor(lending_group,levels=c("Low","Lower-Middle","Upper-Middle","High","NA")),color=factor(lending_group,levels=c("Low","Lower-Middle","Upper-Middle","High","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) +
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  xlim(-300,3000) + 
  xlab(bquote('Optimized Annual Population-Level Reductions in Diet-Attributable Emissions (Million kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_reductions_optimized <- impact_data %>%
  ggplot(aes(greatest_population_reduction_kg_co2e,fill=factor(development_group,levels=c("Low","Medium","High","Very High","NA")),color=factor(development_group,levels=c("Low","Medium","High","Very High","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) +
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  xlim(-300,3000) +
  xlab(bquote('Optimized Annual Population-Level Reductions in Diet-Attributable Emissions (Million kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_reductions_optimized,development_group_reductions_optimized,
          nrow=2,
          labels=c("A","B"))
```
## Lending- and Development-Group Membership, Dichotomized

```{r}
impact_data %>%
  count(lending_group_dichotomy)
```

```{r}
lending_group_membership_dichotomized <- spatial_impact_data %>%
  ggplot(aes(x=long,y=lat,group=group,fill=factor(lending_group_dichotomy,levels=c("Lower","Higher","NA")))) + 
  geom_polygon(color="black",size=0.125) +
  scale_fill_brewer(palette="Set2",na.value="white",name="Lending Group",labels=c("Lower (n=43)","Higher (n=77)","NA")) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
impact_data %>%
  count(development_group_dichotomy)
```

```{r}
development_group_membership_dichotomized <- spatial_impact_data %>%
  ggplot(aes(x=long,y=lat,group=group,fill=factor(development_group_dichotomy,levels=c("Global South","Global North","NA")))) + 
  geom_polygon(color="black",size=0.125,alpha=0.75) +
  scale_fill_brewer(palette="Set3",na.value="white",name="Development Group",labels=c("Global South (n=62)","Global North (n=58)","NA")) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_membership_dichotomized,development_group_membership_dichotomized,
          nrow=2,
          labels=c("A","B"))
```

## Lending- and Development-Group Distributions, Dichotomized

lending_group_distribution_dichotomized

```{r}
lending_group_baseline_distribution_dichotomized <- impact_data %>%
  ggplot(aes(baseline_population_kg_co2e,fill=factor(lending_group_dichotomy,levels=c("Lower","Higher","NA")),color=factor(lending_group_dichotomy,levels=c("Lower","Higher","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set2",name="Lending Group",labels=c("Lower (n=43)","Higher (n=77)","NA")) +
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Lower (n=43)","Higher (n=77)","NA")) + 
  xlim(-800,2500) + 
  xlab(bquote('Annual Population-Level, Diet-Attributable Emissions at Baseline (Millions of kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_baseline_distribution_dichotomized <- impact_data %>%
  ggplot(aes(baseline_population_kg_co2e,fill=factor(development_group_dichotomy,levels=c("Global South","Global North","NA")),color=factor(development_group_dichotomy,levels=c("Global South","Global North","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set3",name="Development Group",labels=c("Global South (n=62)","Global North (n=58)","NA")) +
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Global South (n=62)","Global North (n=58)","NA")) + 
  xlim(-400,1500) +
  xlab(bquote('Annual Population-Level, Diet-Attributable Emissions at Baseline (Millions of kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_baseline_distribution_dichotomized,development_group_baseline_distribution_dichotomized,
          nrow=2,
          labels=c("A","B"))
```

## Groupwise Comparisons, Dichotomized

```{r}
lending_group_reductions_distribution_dichotomized <- impact_data %>%
  ggplot(aes(greatest_population_reduction_kg_co2e,fill=factor(lending_group_dichotomy,levels=c("Lower","Higher","NA")),color=factor(lending_group_dichotomy,levels=c("Lower","Higher","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set2",name="Lending Group",labels=c("Lower (n=43)","Higher (n=77)","NA")) +
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Lower (n=43)","Higher (n=77)","NA")) + 
  xlim(-300,3000) + 
  xlab(bquote('Optimized Annual Population-Level Reductions in Diet-Attributable Emissions (Million kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_reductions_distribution_dichotomized <- impact_data %>%
  ggplot(aes(greatest_population_reduction_kg_co2e,fill=factor(development_group_dichotomy,levels=c("Global South","Global North","NA")),color=factor(development_group_dichotomy,levels=c("Global South","Global North","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set3",name="Development Group",labels=c("Global South (n=62)","Global North (n=58)","NA")) +
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Global South (n=62)","Global North (n=58)","NA")) + 
  xlim(-300,3000) +
  xlab(bquote('Optimized Annual Population-Level Reductions in Diet-Attributable Emissions (Million kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_reductions_distribution_dichotomized,development_group_reductions_distribution_dichotomized,
          nrow=2,
          labels=c("A","B"))
```

```{r}
impact_data %>%
  group_by(lending_group_dichotomy) %>%
  summarize(mean=mean(greatest_population_reduction_kg_co2e),sd=sd(greatest_population_reduction_kg_co2e))
```

```{r}
impact_data %>%
  group_by(development_group_dichotomy) %>%
  summarize(mean=mean(greatest_population_reduction_kg_co2e),sd=sd(greatest_population_reduction_kg_co2e))
```

## Global 



## Choropleths



## Residual Code Chunks

```{r}
impact_data %>%
  ggplot(aes(factor(lending_group),baseline_population_kg_co2e)) + 
  geom_violin(scale="width") + 
  stat_summary(fun.y=mean, geom="point", shape=21, size=2) +
  coord_flip()
```


```{r}
impact_data %>%
  ggplot(aes(factor(development_group),baseline_population_kg_co2e)) + 
  geom_violin(scale="width") + 
  stat_summary(fun.y=mean, geom="point", shape=21, size=2) +
  coord_flip()
```

```{r}
impact_data %>% 
ggplot(aes(x=baseline_population_kg_co2e,y=development_group,fill=stat(x))) +
  geom_density_ridges_gradient() +
  scale_fill_viridis_c(option="C")
```
```{r}
impact_data %>% 
ggplot(aes(x=baseline_population_kg_co2e,y=lending_group,fill=stat(x))) +
  geom_density_ridges_gradient(alpha=0.1) +
  scale_fill_viridis_c(option="C")
```


### Average Reduction










```{r}
ggplot(spatial_impact_data,aes(x=long,y=lat,fill=proportion_school_aged_enrolled,group=group)) + 
  geom_polygon(color="black",size=0.125,alpha=0.66) + 
  scale_fill_continuous_sequential(labels=function(x)x/1000000,name="Millions Enrolled",palette="Purple-Blue",na.value="white",breaks=c(0,6000000,12000000,18000000,24000000,30000000),alpha=0.66) +
  guides(fill=guide_colorbar(title.position="top",title.hjust=0.5)) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  ggtitle("Enrollment Total") +
  theme(legend.position="bottom",panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.key.width=unit(3.5,"cm"))
```



scale_fill_gradient(alpha=0.66,name=bquote('Kilograms CO'[2]*'e'),colors="z2",trans="reverse",na.value="white",labels=scales::comma,breaks=c(750,1500,2250,3000,3750)) +
  guides(fill=guide_colorbar(reverse=TRUE,title.position="top",title.hjust=0.5)) +
  
```{r}
ggplot(spatial_impact_data,aes(x=long,y=lat,fill=eat_lancet_population_percent_reduction_kg_co2e
,group=group)) + 
  geom_polygon(color="black",size=0.125,alpha=0.66) + 
  scale_fill_gradient(low="palegreen",high="palegreen4",na.value="white") +
  guides(fill=guide_colorbar(reverse=TRUE,title.position="top",title.hjust=0.5)) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  ggtitle("Diet-Attributable Greenhouse Gas Footprint at Baseline") +
  theme(legend.position="bottom",panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.key.width=unit(3.5,"cm"))
```

```{r}
ggplot(spatial_impact_data,aes(x=long,y=lat,fill=eat_lancet_population_reduction_kg_co2e
,group=group)) + 
  geom_polygon(color="black",size=0.125,alpha=0.66) + 
  scale_fill_viridis_c(alpha=0.66,name=bquote('Kilograms CO'[2]*'e'),option="F",trans="reverse",na.value="white",labels=scales::comma,breaks=c(750,1500,2250,3000,3750)) +
  guides(fill=guide_colorbar(reverse=TRUE,title.position="top",title.hjust=0.5)) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  ggtitle("Diet-Attributable Greenhouse Gas Footprint at Baseline") +
  theme(legend.position="bottom",panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.key.width=unit(3.5,"cm"))
```



