---
title: "Data Analysis and Visualization"
output: github_document
date: "Last updated: June 12, 2024"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package Loading

Here, we load in the various packages that will be required to support our analyses and the corresponding visualizations we will develop.

```{r}
library(tidyverse)
library(viridis)
library(RColorBrewer)
library(colorspace)
library(ggpubr)
library(ggridges)
library(forcats)
library(lazyeval)
```

## Data Loading

Here, we load in the data in the two formats we provided at the end of our cleaning script: one suited for spatial visualization and analysis and one not. 

```{r}
impact_data <- read.csv("/Users/kenjinchang/github/university-impact-model/data/model-output/university-impact-model.csv")
spatial_impact_data <- read.csv("/Users/kenjinchang/github/university-impact-model/data/model-output/university-impact-model-shapefile.csv")
```

## Nation-State Inclusion 

First, we will generate a figure separating the nation-states included within our analysis from those that were omitted for the various reasons cited in our cleaning script. We will eventually also have to create a complementary flow diagram documenting this exclusion process, whereby nation-states were excluded either (1) because they did not have complete dietary-footprint data across the two identified sources (i.e., publication data for Kim et al. (2020) and publication data for Semba et al. (2020)), (2) because they did not have the

```{r}
spatial_impact_data %>%
  mutate(inclusion=ifelse(university_enrollment>0,country)) %>%
  ggplot(aes(x=long,y=lat,fill=inclusion,group=group)) + 
  geom_polygon(color="black",size=0.125,alpha=0.75) +
  scale_fill_discrete(h=c(260,260),na.value="white") +
  guides(fill="none") +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  ggtitle("Figure X. Choropleth map indicating the 120 nation-states included in our analyses.") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

## Lending- and Development-Group Membership

```{r}
impact_data %>%
  count(lending_group)
```

```{r}
lending_group_membership <- spatial_impact_data %>%
  ggplot(aes(x=long,y=lat,group=group,fill=factor(lending_group,levels=c("Low","Lower-Middle","Upper-Middle","High","NA")))) + 
  geom_polygon(color="black",size=0.125) +
  scale_fill_brewer(palette="Set2",na.value="white",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
impact_data %>%
  count(development_group)
```

```{r}
development_group_membership <- spatial_impact_data %>%
  ggplot(aes(x=long,y=lat,group=group,fill=factor(development_group,levels=c("Low","Medium","High","Very High","NA")))) + 
  geom_polygon(color="black",size=0.125) +
  scale_fill_brewer(palette="Set3",na.value="white",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```


  ggtitle("Figure X. Choropleth map sorting the 120 nation-states included in our analyses into their corresponding lending- and development-group categories.") +
  
```{r}
ggarrange(lending_group_membership,development_group_membership,
          nrow=2,
          labels=c("A","B"))
```

## Lending- and Development-Group Distributions

First, change population figures to millions kg Co2e


```{r}
impact_data <- impact_data %>%
  mutate(baseline_population_kg_co2e=baseline_population_kg_co2e/1000000) %>%
  mutate(baseline_adjusted_population_kg_co2e=baseline_adjusted_population_kg_co2e/1000000) %>%
  mutate(baseline_oecd_population_kg_co2e=baseline_oecd_population_kg_co2e/1000000) %>%
  mutate(meatless_day_population_kg_co2e=meatless_day_population_kg_co2e/1000000) %>%
  mutate(low_red_meat_population_kg_co2e=low_red_meat_population_kg_co2e/1000000) %>%
  mutate(no_red_meat_population_kg_co2e=no_red_meat_population_kg_co2e/1000000) %>%
  mutate(no_dairy_population_kg_co2e=no_dairy_population_kg_co2e/1000000) %>%
  mutate(pescetarian_population_kg_co2e=pescetarian_population_kg_co2e/1000000) %>%
  mutate(lacto_ovo_vegetarian_population_kg_co2e=lacto_ovo_vegetarian_population_kg_co2e/1000000) %>%
  mutate(eat_lancet_population_kg_co2e=eat_lancet_population_kg_co2e/1000000) %>%
  mutate(two_thirds_vegan_population_kg_co2e=two_thirds_vegan_population_kg_co2e/1000000) %>%
  mutate(vegan_population_kg_co2e=vegan_population_kg_co2e/1000000) %>%
  mutate(baseline_adjusted_population_reduction_kg_co2e=baseline_adjusted_population_reduction_kg_co2e/1000000) %>%
  mutate(baseline_oecd_population_reduction_kg_co2e=baseline_oecd_population_reduction_kg_co2e/1000000) %>%
  mutate(meatless_day_population_reduction_kg_co2e=meatless_day_population_reduction_kg_co2e/1000000) %>%
  mutate(low_red_meat_population_reduction_kg_co2e=low_red_meat_population_reduction_kg_co2e/1000000) %>%
  mutate(no_red_meat_population_reduction_kg_co2e=no_red_meat_population_reduction_kg_co2e/1000000) %>%
  mutate(no_dairy_population_reduction_kg_co2e=no_dairy_population_reduction_kg_co2e/1000000) %>%
  mutate(pescetarian_population_reduction_kg_co2e=pescetarian_population_reduction_kg_co2e/1000000) %>%
  mutate(lacto_ovo_vegetarian_population_reduction_kg_co2e=lacto_ovo_vegetarian_population_reduction_kg_co2e/1000000) %>%
  mutate(eat_lancet_population_reduction_kg_co2e=eat_lancet_population_reduction_kg_co2e/1000000) %>%
  mutate(two_thirds_vegan_population_reduction_kg_co2e=two_thirds_vegan_population_reduction_kg_co2e/1000000) %>%
  mutate(vegan_population_reduction_kg_co2e=vegan_population_reduction_kg_co2e/1000000)
```


```{r}
lending_group_baseline_distribution <- impact_data %>%
  ggplot(aes(baseline_population_kg_co2e,fill=factor(lending_group,levels=c("Low","Lower-Middle","Upper-Middle","High","NA")),color=factor(lending_group,levels=c("Low","Lower-Middle","Upper-Middle","High","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) +
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  xlim(-800,2500) + 
  xlab(bquote('Annual Population-Level, Diet-Attributable Emissions at Baseline (Million kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_baseline_distribution <- impact_data %>%
  ggplot(aes(baseline_population_kg_co2e,fill=factor(development_group,levels=c("Low","Medium","High","Very High","NA")),color=factor(development_group,levels=c("Low","Medium","High","Very High","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) +
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  xlim(-400,1500) +
  xlab(bquote('Annual Population-Level, Diet-Attributable Emissions at Baseline (Million kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_baseline_distribution,development_group_baseline_distribution,
          nrow=2,
          labels=c("A","B"))
```


```{r}
impact_data %>%
  group_by(lending_group) %>%
  summarize(mean=mean(baseline_population_kg_co2e),sd=sd(baseline_population_kg_co2e)) 
```


```{r}
impact_data %>%
  group_by(development_group) %>%
  summarize(mean=mean(baseline_population_kg_co2e),sd=sd(baseline_population_kg_co2e)) 
```

## Descriptive Results 

```{r}
impact_data %>%
  select(country,proportion_school_aged) %>%
  summarise(mean(proportion_school_aged))
```


```{r}
lending_group_mean_percent_reduction <- impact_data %>%
  mutate(mean_population_percent_reduction_kg_co2e=(meatless_day_population_percent_reduction_kg_co2e+low_red_meat_population_percent_reduction_kg_co2e+no_red_meat_day_population_percent_reduction_kg_co2e+no_dairy_population_percent_reduction_kg_co2e+pescetarian_population_percent_reduction_kg_co2e+lacto_ovo_vegetarian_population_percent_reduction_kg_co2e+eat_lancet_population_percent_reduction_kg_co2e+two_thirds_vegan_population_percent_reduction_kg_co2e+vegan_population_percent_reduction_kg_co2e)/9) %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,mean_population_percent_reduction_kg_co2e),y=mean_population_percent_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Average Percent-Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_mean_percent_reduction <- impact_data %>%
  mutate(mean_population_percent_reduction_kg_co2e=(meatless_day_population_percent_reduction_kg_co2e+low_red_meat_population_percent_reduction_kg_co2e+no_red_meat_day_population_percent_reduction_kg_co2e+no_dairy_population_percent_reduction_kg_co2e+pescetarian_population_percent_reduction_kg_co2e+lacto_ovo_vegetarian_population_percent_reduction_kg_co2e+eat_lancet_population_percent_reduction_kg_co2e+two_thirds_vegan_population_percent_reduction_kg_co2e+vegan_population_percent_reduction_kg_co2e)/9) %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,mean_population_percent_reduction_kg_co2e),y=mean_population_percent_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Average Percent-Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_mean_percent_reduction,development_group_mean_percent_reduction,
          nrow=2,
          labels=c("A","B"))
```

```{r}
lending_group_mean_absolute_reduction <- impact_data %>%
  mutate(mean_population_reduction_kg_co2e=(meatless_day_population_reduction_kg_co2e+low_red_meat_population_reduction_kg_co2e+no_red_meat_population_reduction_kg_co2e+no_dairy_population_reduction_kg_co2e+pescetarian_population_reduction_kg_co2e+lacto_ovo_vegetarian_population_reduction_kg_co2e+eat_lancet_population_reduction_kg_co2e+two_thirds_vegan_population_reduction_kg_co2e+vegan_population_reduction_kg_co2e)/9) %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,mean_population_reduction_kg_co2e),y=mean_population_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Average Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_mean_absolute_reduction <- impact_data %>%
  mutate(mean_population_reduction_kg_co2e=(meatless_day_population_reduction_kg_co2e+low_red_meat_population_reduction_kg_co2e+no_red_meat_population_reduction_kg_co2e+no_dairy_population_reduction_kg_co2e+pescetarian_population_reduction_kg_co2e+lacto_ovo_vegetarian_population_reduction_kg_co2e+eat_lancet_population_reduction_kg_co2e+two_thirds_vegan_population_reduction_kg_co2e+vegan_population_reduction_kg_co2e)/9) %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,mean_population_reduction_kg_co2e),y=mean_population_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Average Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```


```{r}
ggarrange(lending_group_mean_absolute_reduction,development_group_mean_absolute_reduction,
          nrow=2,
          labels=c("A","B"))
```

Because the average reduction across the nine arbitrarily chosen scenarios may not be particularly useful, we may want to, instead, look at the returns associated with the most impactful scenarios across the various nation-states included within our analysis. 

For now, though, let us look first at the top ten performing nation-states when taking the average across the scenarios.

```{r}
impact_data %>%
  mutate(mean_population_reduction_kg_co2e=(meatless_day_population_reduction_kg_co2e+low_red_meat_population_reduction_kg_co2e+no_red_meat_population_reduction_kg_co2e+no_dairy_population_reduction_kg_co2e+pescetarian_population_reduction_kg_co2e+lacto_ovo_vegetarian_population_reduction_kg_co2e+eat_lancet_population_reduction_kg_co2e+two_thirds_vegan_population_reduction_kg_co2e+vegan_population_reduction_kg_co2e)/9) %>%
  select(country,mean_population_reduction_kg_co2e) %>%
  arrange(desc(mean_population_reduction_kg_co2e)) %>%
  head(10)
```

As described previously, we will now run a similar set of analyses for the 120 included nation-states - this time, for each of their optimal change scenarios. - should spot check this

```{r}
impact_data <- impact_data %>%
  mutate(greatest_population_reduction_kg_co2e=pmax(meatless_day_population_reduction_kg_co2e,low_red_meat_population_reduction_kg_co2e,no_red_meat_population_reduction_kg_co2e,no_dairy_population_reduction_kg_co2e,pescetarian_population_reduction_kg_co2e,lacto_ovo_vegetarian_population_reduction_kg_co2e,eat_lancet_population_reduction_kg_co2e,two_thirds_vegan_population_reduction_kg_co2e,vegan_population_reduction_kg_co2e))
```

```{r}
impact_data <- impact_data %>%
  mutate(greatest_reduction_diet=case_when(greatest_population_reduction_kg_co2e==meatless_day_population_reduction_kg_co2e~"Meatless Day",
                                           greatest_population_reduction_kg_co2e==low_red_meat_population_reduction_kg_co2e~"Low Red Meat",
                                           greatest_population_reduction_kg_co2e==no_red_meat_population_reduction_kg_co2e~"No Red Meat",
                                           greatest_population_reduction_kg_co2e==no_dairy_population_reduction_kg_co2e~"No Dairy",
                                           greatest_population_reduction_kg_co2e==pescetarian_population_reduction_kg_co2e~"Pescetarian",
                                           greatest_population_reduction_kg_co2e==lacto_ovo_vegetarian_population_reduction_kg_co2e~"Lacto-Ovo Vegetarian",
                                           greatest_population_reduction_kg_co2e==eat_lancet_population_reduction_kg_co2e~"EAT Lancet",
                                           greatest_population_reduction_kg_co2e==two_thirds_vegan_population_reduction_kg_co2e~"Two-Thirds Vegan",
                                           greatest_population_reduction_kg_co2e==vegan_population_reduction_kg_co2e~"Vegan"))
```


With this complete, we can now calculate the "technical potential" of university-based dietary interventions, which is to say, the total reductions in diet-attributable greenhouse gas emission (represented in kg CO2e) if the target populations were to change their behaviors as intended, per Nielsen and colleagues (2024).

```{r}
impact_data %>%
  summarize(sum(greatest_population_reduction_kg_co2e))
```
We can also identify the top 10 performing nation-states, as we did before - this time, for the optimized scenarios.

```{r}
impact_data %>%
  select(country,greatest_population_reduction_kg_co2e) %>%
  arrange(desc(greatest_population_reduction_kg_co2e)) %>%
  head(10)
```

Will have to move this to the most appropriate section later, BUT, we'll want to use similar code to look at how this varies across groupings 

```{r}
impact_data %>%
  select(country,lending_group,greatest_population_reduction_kg_co2e) %>%
  group_by(lending_group) %>%
  arrange(desc(greatest_population_reduction_kg_co2e)) 
```


estimates the total global impact if the most ideal dietary change occurred - should do same for relative change (percent reduction)

```{r}
lending_group_optimized_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,greatest_population_reduction_kg_co2e),y=greatest_population_reduction_kg_co2e,fill=lending_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```
  
```{r}
development_group_optimized_absolute_reduction <- impact_data %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,greatest_population_reduction_kg_co2e),y=greatest_population_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```
  
```{r}
ggarrange(lending_group_optimized_absolute_reduction,development_group_optimized_absolute_reduction,
          nrow=2,
          labels=c("A","B"))
```


```{r}
lending_group_optimized_percent_reduction <- impact_data %>% 
  mutate(optimal_diet_population_percent_reduction_kg_co2e=(baseline_population_kg_co2e-greatest_population_reduction_kg_co2e)/baseline_population_kg_co2e) %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,optimal_diet_population_percent_reduction_kg_co2e),y=optimal_diet_population_percent_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Average Percent-Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_optimized_percent_reduction <- impact_data %>% 
  mutate(optimal_diet_population_percent_reduction_kg_co2e=(baseline_population_kg_co2e-greatest_population_reduction_kg_co2e)/baseline_population_kg_co2e) %>%
  ggplot(aes(x=fct_reorder(country_alpha_three,optimal_diet_population_percent_reduction_kg_co2e),y=optimal_diet_population_percent_reduction_kg_co2e,fill=development_group)) +
  geom_col() + 
  xlab("Nation-State") + 
  ylab("Average Percent-Reduction in Diet-Attributable Emissions") + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_optimized_percent_reduction,development_group_optimized_percent_reduction,
          nrow=2,
          labels=c("A","B"))
```
 
Something not adding up with relative change 

```{r}
impact_data %>%
  mutate(optimal_diet_population_percent_reduction_kg_co2e=(baseline_population_kg_co2e-greatest_population_reduction_kg_co2e)/baseline_population_kg_co2e) %>%
  select(country,vegan_population_percent_reduction_kg_co2e,optimal_diet_population_percent_reduction_kg_co2e,vegan_population_reduction_kg_co2e,greatest_population_reduction_kg_co2e)
```


NEXT STEP WILL BE TO LOOK AT RELATIVE CHANGE FROM OPTIMIZED SCENARIO AND ALSO PROBABLY MOVE DICHOTOMIZED TO LOWER SECTIONS - 
  
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  
  
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 

xlab("Nation-State") + 
  ylab("Average Reduction in Diet-Attributable Emissions") + 
  
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1),legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))

## Groupwise Comparisons

```{r}
impact_data %>%
  group_by(lending_group) %>%
  summarize(mean=mean(greatest_population_reduction_kg_co2e),sd=sd(greatest_population_reduction_kg_co2e))
```

```{r}
impact_data %>%
  group_by(development_group) %>%
  summarize(mean=mean(greatest_population_reduction_kg_co2e),sd=sd(greatest_population_reduction_kg_co2e))
```

```{r}
lending_group_reductions_optimized <- impact_data %>%
  ggplot(aes(greatest_population_reduction_kg_co2e,fill=factor(lending_group,levels=c("Low","Lower-Middle","Upper-Middle","High","NA")),color=factor(lending_group,levels=c("Low","Lower-Middle","Upper-Middle","High","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) +
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Low (n=13)","Lower Middle (n=30)","Upper Middle (n=31)","High (n=46)","NA")) + 
  xlim(-300,3000) + 
  xlab(bquote('Optimized Annual Population-Level Reductions in Diet-Attributable Emissions (Million kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_reductions_optimized <- impact_data %>%
  ggplot(aes(greatest_population_reduction_kg_co2e,fill=factor(development_group,levels=c("Low","Medium","High","Very High","NA")),color=factor(development_group,levels=c("Low","Medium","High","Very High","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) +
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Low (n=16)","Medium (n=16)","High (n=30)","Very High (n=58)","NA")) + 
  xlim(-300,3000) +
  xlab(bquote('Optimized Annual Population-Level Reductions in Diet-Attributable Emissions (Million kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_reductions_optimized,development_group_reductions_optimized,
          nrow=2,
          labels=c("A","B"))
```
## Lending- and Development-Group Membership, Dichotomized

```{r}
impact_data %>%
  count(lending_group_dichotomy)
```

```{r}
lending_group_membership_dichotomized <- spatial_impact_data %>%
  ggplot(aes(x=long,y=lat,group=group,fill=factor(lending_group_dichotomy,levels=c("Lower","Higher","NA")))) + 
  geom_polygon(color="black",size=0.125) +
  scale_fill_brewer(palette="Set2",na.value="white",name="Lending Group",labels=c("Lower (n=43)","Higher (n=77)","NA")) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
impact_data %>%
  count(development_group_dichotomy)
```

```{r}
development_group_membership_dichotomized <- spatial_impact_data %>%
  ggplot(aes(x=long,y=lat,group=group,fill=factor(development_group_dichotomy,levels=c("Global South","Global North","NA")))) + 
  geom_polygon(color="black",size=0.125,alpha=0.75) +
  scale_fill_brewer(palette="Set3",na.value="white",name="Development Group",labels=c("Global South (n=62)","Global North (n=58)","NA")) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_membership_dichotomized,development_group_membership_dichotomized,
          nrow=2,
          labels=c("A","B"))
```

## Lending- and Development-Group Distributions, Dichotomized

lending_group_distribution_dichotomized

```{r}
lending_group_baseline_distribution_dichotomized <- impact_data %>%
  ggplot(aes(baseline_population_kg_co2e,fill=factor(lending_group_dichotomy,levels=c("Lower","Higher","NA")),color=factor(lending_group_dichotomy,levels=c("Lower","Higher","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set2",name="Lending Group",labels=c("Lower (n=43)","Higher (n=77)","NA")) +
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Lower (n=43)","Higher (n=77)","NA")) + 
  xlim(-800,2500) + 
  xlab(bquote('Annual Population-Level, Diet-Attributable Emissions at Baseline (Millions of kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_baseline_distribution_dichotomized <- impact_data %>%
  ggplot(aes(baseline_population_kg_co2e,fill=factor(development_group_dichotomy,levels=c("Global South","Global North","NA")),color=factor(development_group_dichotomy,levels=c("Global South","Global North","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set3",name="Development Group",labels=c("Global South (n=62)","Global North (n=58)","NA")) +
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Global South (n=62)","Global North (n=58)","NA")) + 
  xlim(-400,1500) +
  xlab(bquote('Annual Population-Level, Diet-Attributable Emissions at Baseline (Millions of kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_baseline_distribution_dichotomized,development_group_baseline_distribution_dichotomized,
          nrow=2,
          labels=c("A","B"))
```

## Groupwise Comparisons, Dichotomized

```{r}
lending_group_reductions_distribution_dichotomized <- impact_data %>%
  ggplot(aes(greatest_population_reduction_kg_co2e,fill=factor(lending_group_dichotomy,levels=c("Lower","Higher","NA")),color=factor(lending_group_dichotomy,levels=c("Lower","Higher","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set2",name="Lending Group",labels=c("Lower (n=43)","Higher (n=77)","NA")) +
  scale_fill_brewer(palette="Set2",name="Lending Group",labels=c("Lower (n=43)","Higher (n=77)","NA")) + 
  xlim(-300,3000) + 
  xlab(bquote('Optimized Annual Population-Level Reductions in Diet-Attributable Emissions (Million kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
development_group_reductions_distribution_dichotomized <- impact_data %>%
  ggplot(aes(greatest_population_reduction_kg_co2e,fill=factor(development_group_dichotomy,levels=c("Global South","Global North","NA")),color=factor(development_group_dichotomy,levels=c("Global South","Global North","NA")))) + 
  geom_density(alpha=0.75) +
  scale_color_brewer(palette="Set3",name="Development Group",labels=c("Global South (n=62)","Global North (n=58)","NA")) +
  scale_fill_brewer(palette="Set3",name="Development Group",labels=c("Global South (n=62)","Global North (n=58)","NA")) + 
  xlim(-300,3000) +
  xlab(bquote('Optimized Annual Population-Level Reductions in Diet-Attributable Emissions (Million kg CO'[2]*'e)')) +
  ylab("Density") +
  theme(legend.position="bottom",legend.justification="right",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
ggarrange(lending_group_reductions_distribution_dichotomized,development_group_reductions_distribution_dichotomized,
          nrow=2,
          labels=c("A","B"))
```

```{r}
impact_data %>%
  group_by(lending_group_dichotomy) %>%
  summarize(mean=mean(greatest_population_reduction_kg_co2e),sd=sd(greatest_population_reduction_kg_co2e))
```

```{r}
impact_data %>%
  group_by(development_group_dichotomy) %>%
  summarize(mean=mean(greatest_population_reduction_kg_co2e),sd=sd(greatest_population_reduction_kg_co2e))
```

## Global 



## Choropleths



## Residual Code Chunks

```{r}
impact_data %>%
  ggplot(aes(factor(lending_group),baseline_population_kg_co2e)) + 
  geom_violin(scale="width") + 
  stat_summary(fun.y=mean, geom="point", shape=21, size=2) +
  coord_flip()
```


```{r}
impact_data %>%
  ggplot(aes(factor(development_group),baseline_population_kg_co2e)) + 
  geom_violin(scale="width") + 
  stat_summary(fun.y=mean, geom="point", shape=21, size=2) +
  coord_flip()
```

```{r}
impact_data %>% 
ggplot(aes(x=baseline_population_kg_co2e,y=development_group,fill=stat(x))) +
  geom_density_ridges_gradient() +
  scale_fill_viridis_c(option="C")
```
```{r}
impact_data %>% 
ggplot(aes(x=baseline_population_kg_co2e,y=lending_group,fill=stat(x))) +
  geom_density_ridges_gradient(alpha=0.1) +
  scale_fill_viridis_c(option="C")
```


### Average Reduction










```{r}
ggplot(spatial_impact_data,aes(x=long,y=lat,fill=proportion_school_aged_enrolled,group=group)) + 
  geom_polygon(color="black",size=0.125,alpha=0.66) + 
  scale_fill_continuous_sequential(labels=function(x)x/1000000,name="Millions Enrolled",palette="Purple-Blue",na.value="white",breaks=c(0,6000000,12000000,18000000,24000000,30000000),alpha=0.66) +
  guides(fill=guide_colorbar(title.position="top",title.hjust=0.5)) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  ggtitle("Enrollment Total") +
  theme(legend.position="bottom",panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.key.width=unit(3.5,"cm"))
```



scale_fill_gradient(alpha=0.66,name=bquote('Kilograms CO'[2]*'e'),colors="z2",trans="reverse",na.value="white",labels=scales::comma,breaks=c(750,1500,2250,3000,3750)) +
  guides(fill=guide_colorbar(reverse=TRUE,title.position="top",title.hjust=0.5)) +
  
```{r}
ggplot(spatial_impact_data,aes(x=long,y=lat,fill=eat_lancet_population_percent_reduction_kg_co2e
,group=group)) + 
  geom_polygon(color="black",size=0.125,alpha=0.66) + 
  scale_fill_gradient(low="palegreen",high="palegreen4",na.value="white") +
  guides(fill=guide_colorbar(reverse=TRUE,title.position="top",title.hjust=0.5)) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  ggtitle("Diet-Attributable Greenhouse Gas Footprint at Baseline") +
  theme(legend.position="bottom",panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.key.width=unit(3.5,"cm"))
```

```{r}
ggplot(spatial_impact_data,aes(x=long,y=lat,fill=eat_lancet_population_reduction_kg_co2e
,group=group)) + 
  geom_polygon(color="black",size=0.125,alpha=0.66) + 
  scale_fill_viridis_c(alpha=0.66,name=bquote('Kilograms CO'[2]*'e'),option="F",trans="reverse",na.value="white",labels=scales::comma,breaks=c(750,1500,2250,3000,3750)) +
  guides(fill=guide_colorbar(reverse=TRUE,title.position="top",title.hjust=0.5)) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  ggtitle("Diet-Attributable Greenhouse Gas Footprint at Baseline") +
  theme(legend.position="bottom",panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.key.width=unit(3.5,"cm"))
```



