---
title: "Data Cleaning and Aggregation"
output: github_document
date: "Last updated: April 29, 2024"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package Loading

```{r}
library(tidyverse)
library(ggpubr)
```
## Data Loading

There are three principal data inputs needed to populate our impact model:

* Shape-File Data
* Dietary-Footprint Data
* University-Enrollment Data

The shape-file data we will be using is local to the `maps` package within the `tidyverse` collection. As such, we can assign the corresponding vector as an object within our environment and write it into the `parent-files` folder of our repository, using the following:

```{r}
shapefile_data <- map_data("world")
write.csv(shapefile_data,file="/Users/kenjinchang/github/university-impact-model/data/parent-files/shapefile_data_by_country.csv")
```

With this step complete, we can now move on to loading in the remaining two data inputs. These include (1) the publication data from "Country-specific dietary shifts to mitigate climate and water crises" (Kim et al., 2020), which was retrieved via the Digital Commons using this [project link](https://data.mendeley.com/datasets/g8n8w8snmj/3), and (2) the customized indicator report generated on April 19, 2024 from the [EdStats database](https://databank.worldbank.org/reports.aspx?source=Education%20Statistics).

```{r}
dietary_footprint_data <- read.csv("/Users/kenjinchang/github/university-impact-model/data/parent-files/dietary_footprints_by_country.csv")
university_enrollment_data <- read.csv("/Users/kenjinchang/github/university-impact-model/data/parent-files/education_data_by_country.csv")
```

Before we can consolidate the relevant information from these individual data inputs into a single matrix, we will first need to make a series of adjustments in preparation for our spatial join. In the following sections, we document each of these steps, the motivations for doing them, and the code chunks used to perform the described transformations.

## Adjusting the Shape-File Data

Because the directory of nation-states used in the `maps` package does not correspond with the country designations used in the remaining two data inputs, we will need to adjust how these areas are geographically and politically represented within our shape-file data.

To ensure consistency in the naming conventions and spatial boundaries adopted across three leveraged data sources, we will follow the guidelines outlined by the [International Organizaation for Standardization (ISO)](https://www.iso.org/iso-3166-country-codes.html).

Using the instructions provided by Thomas Haslam in his 2021 [RPubs entry](https://rpubs.com/Thom_JH/798825), we will begin this process by addressing what he refers to as the "easy cases" first.

These refer to the 13 instances where the names of the nation-states listed under the `region` variable in the `maps` package are misaligned with the names of the nation-states listed under the `country` variable in the `Gapminder` dataset—a commonly used data source that happens to be synchronized with [ISO-3166 naming standards](https://www.iso.org/iso-3166-country-codes.html). 

```{r}
shapefile_data <- shapefile_data %>% 
  rename(country=region) %>%
  mutate(country=case_when(country=="Macedonia"~"North Macedonia",
                           country=="Ivory Coast"~"Cote d'Ivoire",
                           country=="Democratic Republic of the Congo"~"Congo, Dem. Rep.",
                           country=="Republic of Congo"~"Congo, Rep.",
                           country=="UK"~"United Kingdom",
                           country=="USA"~"United States",
                           country=="Laos"~"Lao",
                           country=="Slovakia"~"Slovak Republic",
                           country=="Saint Lucia"~"St. Lucia",
                           country=="Kyrgyzstan"~"Krygyz Republic",
                           country=="Micronesia"~"Micronesia, Fed. Sts.",
                           country=="Swaziland"~"Eswatini",
                           country=="Virgin Islands"~"Virgin Islands (U.S.)",
                        TRUE~country))
```

For the next group of cases, which Haslam refers to as the "island nations," we will need to aggregate the previously grouped regions of Antigua and Barbuda, St. Kitts and Nevi, Trinidad and Tobago, and St. Vincent and the Grenadines using the following:

```{r}
island_nations <- c("Antigua","Barbuda","Nevis", 
                 "Saint Kitts","Trinidad",
                 "Tobago","Grenadines","Saint Vincent")
island_nations_match <- shapefile_data %>% 
  filter(country %in% island_nations)
island_nations_match %>% distinct(country)
ant_bar <- c(137,138 )
kit_nev <- c(930,931)
tri_tog <- c(1425,1426)
vin_gre <- c(1575,1576,1577)
island_nation_names <- c("Antigua and Barbuda","St. Kitts and Nevis","Trinidad and Tobago","St. Vincent and the Grenadines")
island_nations_match <- island_nations_match %>% 
  mutate(country=case_when(group %in% ant_bar~"Antigua and Barbuda",
                           group %in% kit_nev~"St. Kitts and Nevis",
                           group %in% tri_tog~"Trinidad and Tobago",
                           group %in% vin_gre~"St. Vincent and the Grenadines")) %>% 
  tibble()
island_nations_match %>%
  distinct(country) 
shapefile_data <- shapefile_data %>%
  filter(!country %in% island_nation_names)
shapefile_data <- shapefile_data %>% 
  bind_rows(island_nations_match) %>%
  arrange(country) %>%
  tibble()
```

Now, we move on to the final two cases pertinent to our impact model. Haslam refers to these instances as "subregion promotion," and they invol

```{r}
sra_names <- c("Hong Kong","Macao")
hk_mc <- shapefile_data %>% 
  filter(subregion %in% sra_names)
hk_mc <- hk_mc %>%
  mutate(country = case_when(subregion=="Hong Kong"~"Hong Kong, China",
                             subregion=="Macao"~"Macao, China"))
shapefile_data <- shapefile_data %>%
  filter(!subregion %in% sra_names)
shapefile_data <- shapefile_data %>% 
  bind_rows(hk_mc) %>%
  select(-subregion) %>% 
  tibble()
```

With these steps complete, we can now review the countries currently accounted for in our shapefile data.

```{r}
shapefile_data %>% distinct(country)
```

## Adjusting the Dietary-Footprint Data



```{r}
impact_data <- read.csv("/Users/kenjinchang/github/university-impact-model/data/parent-files/dietary_footprints_by_country.csv")
dietary_footprint_data %>% head(6)
```


```{r}
write.csv(impact_data,"~/github/university-impact-model/data/model-output/impact-data.csv")
```

