---
title: "Data Cleaning and Aggregation"
output: github_document
date: "Last updated: April 29, 2024"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package Loading

```{r}
library(tidyverse)
library(ggpubr)
```
## Data Loading

There are three principal data inputs needed to generate our impact model:

* Shape-File Data
* Dietary-Footprint Data
* University-Enrollment Data

The shape-file data we will be using, which is local to the `maps` package within the `tidyverse` collection, can be written into the `parent-files` folder of our respository with the following: 

```{r}
shapefile_data <- map_data("world")
write.csv(shapefile_data,file="/Users/kenjinchang/github/university-impact-model/data/parent-files/shapefile_data_by_country.csv")
```

With the shape-file data now archived, we can  move on to loading in the remaining two data inputs. These include (1) the publication data from "Country-specific dietary shifts to mitigate climate and water crises" (Kim et al., 2020), which was retrieved via the Digital Commons using this [ link](https://data.mendeley.com/datasets/g8n8w8snmj/3), and (2) the customized indicator report created on April 19, 2024 from the [EdStats database](https://databank.worldbank.org/reports.aspx?source=Education%20Statistics).

```{r}
dietary_footprint_data <- read.csv("/Users/kenjinchang/github/university-impact-model/data/parent-files/dietary_footprints_by_country.csv")
university_enrollment_data <- read.csv("/Users/kenjinchang/github/university-impact-model/data/parent-files/education_data_by_country.csv")
```

Before synthesizing the relevant information from these individual inputs into a single data file, we will first need to make a series of adjustments in preparation for our spatial join. In the following sections, we document these steps, their motivations, and the code chunks used to transform them.

## Adjusting the Shape-File Data

Because the directory of nation-states used in the `maps` package does not correspond with the country designations used in the remaining two data sources, we will need to adjust how these areas are geographically and politically represented within our shape-file data.

To ensure consistency in naming, as well as the spatial boundaries used to represent these areas, across three leveraged data sources, we will follow the conventions outlined by the [International Organizaation for Standardization (ISO)](https://www.iso.org/iso-3166-country-codes.html).

Following the instructions provided by Thomas Haslam in his 2021 [RPubs entry](https://rpubs.com/Thom_JH/798825), we will begin this process by first addressing what he refers to as the "easy cases."

These cases refer to the 13 instances where the names of the nation-states listed under the `region` variable in the `maps` package are misaligned with the names of the nation-states listed under the `country` variable in the `Gapminder` dataset—a commonly used data source that happens to be synchronized with [ISO-3166 naming standards](https://www.iso.org/iso-3166-country-codes.html). 

```{r}
shapefile_data <- shapefile_data %>% 
  rename(country=region) %>%
  mutate(country=case_when(country=="Macedonia"~"North Macedonia",
                           country=="Ivory Coast"~"Cote d'Ivoire",
                           country=="Democratic Republic of the Congo"~"Congo, Dem. Rep.",
                           country=="Republic of Congo"~"Congo, Rep.",
                           country=="UK"~"United Kingdom",
                           country=="USA"~"United States",
                           country=="Laos"~"Lao",
                           country=="Slovakia"~"Slovak Republic",
                           country=="Saint Lucia"~"St. Lucia",
                           country=="Kyrgyzstan"~"Krygyz Republic",
                           country=="Micronesia"~"Micronesia, Fed. Sts.",
                           country=="Swaziland"~"Eswatini",
                           country=="Virgin Islands"~"Virgin Islands (U.S.)",
                        TRUE~country))
```

For the next group of cases, which Haslam refers to as the "island nations," we will need to aggregate the previously separated regions of Antigua and Barbuda, St. Kitts and Nevis, Trinidad and Tobago, and St. Vincent and the Grenadines using the following:

```{r}
island_nations <- c("Antigua","Barbuda","Nevis", 
                 "Saint Kitts","Trinidad",
                 "Tobago","Grenadines","Saint Vincent")
island_nations_match <- shapefile_data %>% 
  filter(country %in% island_nations)
island_nations_match %>% distinct(country)
ant_bar <- c(137,138 )
kit_nev <- c(930,931)
tri_tog <- c(1425,1426)
vin_gre <- c(1575,1576,1577)
island_nation_names <- c("Antigua and Barbuda","St. Kitts and Nevis","Trinidad and Tobago","St. Vincent and the Grenadines")
island_nations_match <- island_nations_match %>% 
  mutate(country=case_when(group %in% ant_bar~"Antigua and Barbuda",
                           group %in% kit_nev~"St. Kitts and Nevis",
                           group %in% tri_tog~"Trinidad and Tobago",
                           group %in% vin_gre~"St. Vincent and the Grenadines")) %>% 
  tibble()
island_nations_match %>%
  distinct(country) 
shapefile_data <- shapefile_data %>%
  filter(!country %in% island_nation_names)
shapefile_data <- shapefile_data %>% 
  bind_rows(island_nations_match) %>%
  arrange(country) %>%
  tibble()
```

Now, we move on to the final two cases pertinent to our impact model, which Haslam refers to as "subregion promotion." In the case of the special administrative regions of Hong Kong and Macao, the `maps` package organizes these states as subregions within its country-classification scheme. While this is politically correct, economic and health data from these regions, as Haslam (2021) points out, are often collected and presented separately from that of mainland China. 

In following this practice, we therefore need to adjust this organizational framework to reflect our desire to treat these regions as country-level entities using the naming conventions prescribed by the ISO. We accomplish this using the following: 

```{r}
sra_names <- c("Hong Kong","Macao")
hk_mc <- shapefile_data %>% 
  filter(subregion %in% sra_names)
hk_mc <- hk_mc %>%
  mutate(country = case_when(subregion=="Hong Kong"~"Hong Kong, China",
                             subregion=="Macao"~"Macao, China"))
shapefile_data <- shapefile_data %>%
  filter(!subregion %in% sra_names)
shapefile_data <- shapefile_data %>% 
  bind_rows(hk_mc) %>%
  select(-subregion) %>% 
  tibble()
```

With these steps complete, we can now review the countries currently accounted for in our shape-file data.

```{r}
shapefile_data %>% distinct(country)
```

## Adjusting the Dietary-Footprint Data



```{r}
impact_data <- read.csv("/Users/kenjinchang/github/university-impact-model/data/parent-files/dietary_footprints_by_country.csv")
dietary_footprint_data %>% head(6)
```


```{r}
write.csv(impact_data,"~/github/university-impact-model/data/model-output/impact-data.csv")
```

